---
title: Brian M. Schilder - CV
author: autoCV
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    # keep_md: yes
    # set it to true for a self-contained HTML page but it'll take longer to render
    css: 
      # OVERIDE CERTAIN FUNCTIONS OF CSS
      - css/override.css
      # - !expr autoCV::get_css()
      # DEFAULT FILE
      - resume 
# uncomment this line to produce HTML and PDF in RStudio:
# knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
htmltools::tagList(fontawesome::fa_html_dependency())
library(autoCV) 
```

<!-- Only show sidebar on first page: https://github.com/rstudio/pagedown/issues/147 -->
```{css, echo=FALSE} 
.pagedjs_page:not(:first-of-type) {
  --sidebar-width: 1rem; 
  --main-width: calc(var(--content-width) - var(--sidebar-width));
  --decorator-horizontal-margin: 0.2in;
}
```

<!-- Custom Info -->
```{r}
####Set your working directory ####
# wd <- autoCV::get_data() ## <-- Change this path to where your data is
# knitr::opts_knit$set(root.dir = wd)

####Set title elements ####
name <- "Brian M Schilder"
title <- ", PhD" 
tagline <- "### Passionately pursuing transdisciplinary research to advance human health and knowledge.

*- Below are selected subsets of the [full CV. -](https://bschilder.github.io/CV/CV.pdf)*"
extra <- list()  
logo <- get_logo(
  img = here::here("network/visnetwork.png"), 
                 link = "https://bschilder.github.io/CV/network/visnetwork.html",
  style = "border-radius:30%; margin-left:-15px; opacity:.7",
  width = "60px"
  )
```

# Aside 

```{r, warning=FALSE, message=FALSE, eval=FALSE}
visnet <- build_network(show_plot = FALSE,
                        save_path = here::here("network","visnetwork.html"))
```

## Contact {#contact}

```{r}
parse_profile(types = c("email","website","phone"))
```

## Summary {#summary}

<h4>  
```{r}
build_summary()
```
</h4>

## Table of Contents {#toc}

```{r}
build_toc(items=c("education","skills","publications","preprints","experience","grants"))
```

<hr>

```{r}
build_footer()
```

# Main

```{r}
build_title(name = paste0(name,name),
            tagline = tagline,
            extra = extra, 
            logo = logo, 
            logo_position = "left")
```


## Education {data-icon=`r icon_dict("education")` data-concise="true" #education}

```{r}
parse_education( include=c("logo",
                           "degree",
                           # "program",
                           "focus",
                           "thesis",
                           "institution"))
```


## Core Skills {data-icon=`r icon_dict("skills")` #skills}

```{r}
parse_skills(types = "core")
```

## Publications {data-icon=`r icon_dict("publications")` #publications}

```{r}
parse_publications(types = "publication",
                   name = name)
```

## Preprints {data-icon=`r icon_dict("preprints")` #preprints}

```{r}
parse_publications(types = "preprint",
                   name = name)
```

## Research Experience {data-icon=`r icon_dict("experience")` #experience}

```{r}
parse_experience(types = "research", 
                 select = TRUE,
                 concise = FALSE)
```

## Grants {data-icon=`r icon_dict("grants")` #grants}

```{r}
parse_grants(types = "NA", 
             add_totals = TRUE)
```
